Very Preliminary Draft

### 2021-07-05 article/draft.tex
cosmetic changes

In this article, we focus on MSMP's policies and actions regarding content with low credibility or false information, commonly referred to as {\it Fake News}.\footnote{For an overview on the {\it concept} of {\it Fake News}, we refer the reader to the article The science of fake news by Lazer et al. (2018)~\cite{lazer}.} The {\it Fake News} phenomenon is still ill-defined by the academic community as it encompasses several combined features such as spreading inaccurate, false or misleading information, with or without the intention of influencing or manipulating a target pool of audience. The growth of social networking platforms over the last decade in terms of number of users worldwide and volume of content, has modified the information ecosystem in terms of production of information and its mediation. Many users can now produce and share content which includes news related information, without having to abide by strict editorial processes that ensure accuracy of information and reliability of sources. In particular, false or inaccurate content produced and shared on social networking platforms concerning the political life or public health may have a potentially harmful impact on the society, in the rare event that it goes viral. This gave rise to a set of heterogenous fact-checking policies across mainstream platforms.

@@

During the COVID19 global health pandemic platforms have upgraded their guidelines to include a set of rules to tackle the propagation of potentially harmful content.\footnote{For Facebook, Twitter and Youtube see respectively the following updates: } As each platform is a private company, those {\it new} policies are not coordinated and are implemented in different ways across platforms. Such targeted policies show the willingness of MSMP to enhance the quality of the online conversation, but also sheds light on the lack of specific policies to tackle misinformation in general. {\color{pink} Say what they say they do + partnerships with fact-checkers + algorithms + community,  idea about academic community needs to be able to study this phenomenon and assess the impact of the policies, what effects they have etc.}

@@

%{\color{red} Policies not specific to misinformation, but to enforce laws + things already used for terrorism and hate speech. Intro or/and Discussion. accounts: hard to say suspension for which.} 
% Misinformation : which law ? not defined !

\begin{table}[]
\centering
\begin{tabular}{|l|l|l|l}

\hline
&  \begin{tabular}[c]{@{}l@{}} Application Programming Interface (API)  \end{tabular}                                                                                                                                                                                                                                                                                                                                                                                                                                            &    \multicolumn{1}{l|}{Web Scraping}                                                                                                                                                                   \\ \hline
Facebook & \begin{tabular}[c]{@{}l@{}}\href{https://www.crowdtangle.com}{CrowdTangle}: public content insights tool \\ owned and operated by Facebook. \\ \href{https://buzzsumo.com}{Buzzsumo}: commercial content database  \end{tabular}                                                                                                                                                                                                               &      \multicolumn{1}{l|}{}    
\\ \hline
Twitter  &  \href{https://developer.twitter.com/en/docs/twitter-api/early-access}{Twitter API V2} & \multicolumn{1}{l|}{\href{https://github.com/medialab/minet/blob/master/docs/cli.md\#twitter-scrape}{Minet twitter scrape}}                                                                                                                                                                           \\ \hline
Youtube  &  \href{https://developers.google.com/youtube/v3}{Youtube API V3}      &                                                                                                                            \multicolumn{1}{l|}{}                                                                                                                                                                           \\ \hline
\end{tabular}
\caption{Data collection}
\label{tab1}
\end{table}

@@

\begin{figure}
\centering
	\begin{multicols}{1}
		\includegraphics[scale=0.3]{./img/lifesite.jpg} 
	\end{multicols}
	\begin{multicols}{1}
		\includegraphics[scale=0.3]{./img/lifesite_rolling_7_lifesite.jpg}
	\end{multicols}
\caption{Panel (a): number of Tweets per day of the Twitter account $@Lifesite$ linked to the website lifesitenews.com from January, 2019 until April 2021. Panel (b): number of Tweets per day that have shared a lifesitenews.com URL link from January, 2019 until April 2021. }
\label{fig2}
\end{figure}

@@

\begin{figure}
	\centering
	\begin{multicols}{1}
		\includegraphics[scale=0.25]{./img/oann/fig1_oann.png}
	\end{multicols}
	\begin{multicols}{1}
		\includegraphics[scale=0.25]{./img/oann/fig2_oann.png} 
	\end{multicols}
	\caption{panel (a): Number of Youtube videos uploaded each day by the youtube channel {\it One America news Network} November 1, 2020 and January 1, 2021. Panel (b): accumulated view counts for videos. The metrics correspond to the videos’  publishing date and the data is retrieved from the youtube API with the {\it playlists} and  {\it videos} endpoints. }
	\label{fig1_oann}
\end{figure}

@@

\begin{figure}
	\centering
	\begin{multicols}{1}
		\includegraphics[scale=0.2]{./img/oann/fig3_oann.png}
	\end{multicols}

	\begin{multicols}{1}
		\includegraphics[scale=0.3]{./img/tony/fig3_tony.png}
	\end{multicols}

@@

In this section, we provide one case study of how Facebook can block a URL as part of its policy enforcement tools. The Beauty of life (\href{https://thebl.com/}{thebl.com/}) is a US-based media company that shares pro-Trump views and conspiracy theories such as QAnon.\footnote{ See \href{https://en.wikipedia.org/wiki/The\_Epoch\_Times\#Removal\_of\_The\_BL\_(The\_Beauty\_of\_Life)\_from\_Facebook}{https://en.wikipedia.org/wiki/The\_Epoch\_Times\#Removal\_of\_The\_BL\_(The\_Beauty\_of\_Life)\_from\_Facebook}.} Facebook has announced on December $20$, $2019$ that ``The BL is now banned from Facebook'' for coordinated inauthentic behavior\footnote{\href{https://about.fb.com/news/2019/12/removing-coordinated-inauthentic-behavior-from-georgia-vietnam-and-the-us/}{https://about.fb.com/news/2019/12/removing-coordinated-inauthentic-behavior-from-georgia-vietnam-and-the-us/}.}, which includes using fake accounts that misrepresent one's identity or using methods to artificially boost the popularity of content. Coordinated inauthentic behavior is a distinct phenomenon from disinformation according to Facebook, as ``most of the content shared by coordinated manipulation campaigns isn’t probably false”.\footnote{See: \href{https://about.fb.com/news/2019/10/inauthentic-behavior-policy-update/}{https://about.fb.com/news/2019/10/inauthentic-behavior-policy-update/}.}

@@

As CrowdTangle is tracking posts only from certain public groups and pages, we also used the ``/search/articles'' endpoint of the Buzzsumo API, to gather a richer Facebook dataset. We collected the engagement data for the $14$ $232$ articles crawled by Buzzsumo from the $Infowars$ website between January $1$, $2019$ and December $31$, $2020$.  \footnote{The command can be found here: \href{https://github.com/medialab/truth-and-trust-online-2021/blob/master/code/collect\_facebook\_buzzsumo\_infowars\_data.py}{https://github.com/medialab/truth-and-trust-online-2021/blob/master/code/collect\_facebook\_buzzsumo\_infowars\_data.py}.} We observe that the articles published after May $2$, $2019$ received less Facebook engagement than the ones published before (see figure \ref{infowars2}), with a percentage change of -$97\%$ for the reactions, -$59\%$ for the shares and -$97\%$ for the comments. An increase in engagement was also observed in $2020$. It reinforces the hypothesis that Facebook reduced the reach of posts sharing Infowars links only during a few months in $2019$.

@@

@@

\begin{figure*}
\centering
	\begin{multicols}{1}
		\includegraphics[scale=0.35]{./img/globalresearch/sum_globalresearch.ca_6_months.jpg} 
		\includegraphics[scale=0.35]{./img/globalresearch/engagement_sum_rolling_1_globalresearch.ca.jpg}
	\end{multicols}
\caption{Top panel: daily number of Tweets, excluding retweets, containing the query {\it globalresearch.ca} from January $1$, $2021$ until June $10$, $2021$. Bottom panel: engagement metrics of Tweets containing the query {\it globalresearch.ca} from January $1$, $2021$ until June $10$, $2021$. Data collected via the Twitter API v2 on June $16$, 2021.   }
\label{fig4}
\end{figure*}

@@

\begin{figure*}
\centering	
	\begin{multicols}{1}
		\includegraphics[scale=0.35]{./img/globalresearch/tweet.png} 
		\includegraphics[scale=0.35]{./img/globalresearch/warning.png}
	\end{multicols}
\caption{}
\label{fig4bis}
\end{figure*}

@@

\begin{figure}
	\centering
	\begin{multicols}{1}
		\includegraphics[scale=0.25]{./img/tweets/Capture_2021-07-01.png} 
	\end{multicols}
	\begin{multicols}{1}
		\includegraphics[scale=0.25]{./img/tweets/Capture_2021-07-01_2.png}
	\end{multicols}
	\caption{Tweet ID \href{https://twitter.com/mohsinmalvi19/status/1285866521533861888}{1285866521533861888}. Screenshots taken on July 1, 2021. }
	\label{fig_notice}
\end{figure}

@@

Youtube may provide an information panel for videos with topics that are prone to misinformation like COVID19, moon landing, and climate change.\footnote{See the section ``Information panel giving topical context'' on Youtube Help, Google accessed on June 28, 2021: \href{https://support.google.com/youtube/answer/9004474?hl=en}{support.google.com/youtube/answer/9004474?hl=en}.} The information panel contains main information about the topic from independent third party partners. Youtube states that these panels exist regardless of the video point of view. In addition , these panels are not available in all languages and countries yet. (“Information panel giving topical context”)

Based on a video list (171 videos) checked by fact checkers and marked to have misinformation. We collected the information panels in each video by scrapping the content of the web and connecting to a US server. Four types of information panels were found in the list of visited videos. The first information panel gives info about COVID19 as in Fig \ref{fig9}, the second is about Vaccine as in Fig \ref{fig9} , the third is about Climate change as in Fig \ref{fig9} and last information panel showed on a COVID19 video about the US voting as in Fig \ref{fig9}.

We classified the list of videos examined for the information panel based on its content as in Table \ref{tab2}. The Table shows the number of videos with a panel in each category. For COVID and vaccine related videos more than half of the videos had a panel, nevertheless, we noticed that some videos get uploaded multiple times by different channels under different video titles but others didn’t even though the video was the same. In addition, we noticed for COVID when the video title doesn’t include keywords like (Testing, Pandemic, COVID, coronavirus) , the video wouldn’t have a panel associated with it, and in some cases when the video title have variations of word COVID like (C.O.V.I.D or Cv19) it wouldn’t include a panel either. Therefore, we suspect that youtube is automatically adding panels to the videos based on the video title not the content of the video since many of the videos that didn’t have a panel had the word COVID or coronavirus or vaccine mentioned in the video itself.
For climate change we only examined 18 misleading videos and we found 72\% of them didn’t have a panel. Lastly , for the general health category, we included the videos that weren’t related to COVID but had misinformation in topics like fake cures for cancer, abortion,  and viruses; there was no information panel in all these videos. Therefore, we suspect that youtube just add information panels to  the most controversial topics that can have misleading information like the climate change, COVID19, flat earth and  vaccine.

@@

@@

\begin{table}[]
\begin{tabular}{|c|c|c|}
\hline
\multirow{3}{*}{Rules}                     & \includegraphics[scale=0.05]{./img/fb_logo.png} & https://www.facebook.com/communitystandards/recentupdates/                         \\ \cline{2-3} 
                                           & \includegraphics[scale=0.007]{./img/tw_logo.png}   & https://help.twitter.com/en/rules-and-policies/twitter-rules                       \\ \cline{2-3} 
                                           & \includegraphics[scale=0.03]{./img/yt_logo.png}  & \href{https://www.youtube.com/intl/en\_us/howyoutubeworks/policies/community-guidelines/}{youtube.com/intl/en\_us/howyoutubeworks/policies/community-guidelines/} \\ \hline
\multirow{3}{*}{Rules enforcement }         & \includegraphics[scale=0.05]{./img/fb_logo.png}  & https://transparency.fb.com/data/community-standards-enforcement/                  \\ \cline{2-3} 
                                           & \includegraphics[scale=0.007]{./img/tw_logo.png}   & https://transparency.twitter.com/en/reports/rules-enforcement.html                 \\ \cline{2-3} 
                                           & \includegraphics[scale=0.03]{./img/yt_logo.png}  & https://transparencyreport.google.com/youtube-policy/                              \\ \hline
\multirow{3}{*}{Transparency center}       & \includegraphics[scale=0.05]{./img/fb_logo.png} & https://transparency.fb.com/data/                                                  \\ \cline{2-3} 
                                           & \includegraphics[scale=0.007]{./img/tw_logo.png}   & https://transparency.twitter.com/en/reports.html                                   \\ \cline{2-3} 
                                           & \includegraphics[scale=0.03]{./img/yt_logo.png}  & https://transparencyreport.google.com/?hl=en                                       \\ \hline
\multirow{3}{*}{Policy regarding Covid-19} & \includegraphics[scale=0.05]{./img/fb_logo.png} & https://www.facebook.com/help/230764881494641/                                     \\ \cline{2-3} 
                                           & \includegraphics[scale=0.007]{./img/tw_logo.png}   & https://help.twitter.com/en/rules-and-policies/medical-misinformation-policy       \\ \cline{2-3} 
                                           & \includegraphics[scale=0.03]{./img/yt_logo.png}  & https://support.google.com/youtube/answer/9891785                                  \\ \hline
\end{tabular}
\end{table}

\end{document}

>>>>

In this article, we focus on MSMP's policies and actions regarding content with low credibility or false information, commonly referred to as {\it Fake News}.\footnote{For an overview on the {\it concept} of {\it Fake News}, we refer the reader to the article The science of fake news by Lazer et al. (2018)~\cite{lazer}.} The {\it Fake News} phenomenon is still ill-defined by the academic community as it encompasses several combined features such as spreading inaccurate, false or misleading information, with or without the intention of influencing or manipulating a target pool of audience. The growth of social networking platforms over the last decade in terms of number of users worldwide and volume of content, has modified the information ecosystem in terms of production of information and its mediation. Many users can now produce and share content which includes news related information, without having to abide by strict editorial processes that ensure accuracy of information and reliability of sources. In particular, false or inaccurate content produced and shared on social networking platforms concerning the political life or public health may have a potentially harmful impact on the society, in the rare event that it goes viral. This gave rise to a set of heterogenous fact-checking policies across mainstream platforms.\footnote{For an overview of Facebook's third-party fact checking program see see \href{https://www.facebook.com/journalismproject/programs/third-party-fact-checking/how-it-works}{https://www.facebook.com/journalismproject/programs/third-party-fact-checking/how-it-works}. For an overview of Youtube's policy on fact-checking see:  }

@@

During the COVID19 global health pandemic platforms have upgraded their guidelines to include a set of rules to tackle the propagation of potentially harmful content.\footnote{For Facebook, Twitter and Youtube see respectively the following updates: \href{https://support.google.com/youtube/answer/9891785}{https://support.google.com/youtube/answer/9891785}.} As each platform is a private company, those {\it new} policies are not coordinated and are implemented in different ways across platforms. Such targeted policies show the willingness of MSMP to enhance the quality of the online conversation, but also sheds light on the lack of specific policies to tackle misinformation in general. In particular, policies regarding misinformation are not part of the set of platform rules or community guidelines\footnote{As of July 2021.}. The 2019 report of the Facebook Data Transparency Advisory Group\footnote{See \href{https://law.yale.edu/yls-today/news/facebook-data-transparency-advisory-group-releases-final-report?fbclid=IwAR2xMZr5GdD1GaNpjsXR3\_yeeIR4H9iFASfrni5HKcJVAO5oWA52bvwcZxU}{https://law.yale.edu/yls-today/news/facebook-data-transparency-advisory-group-releases-final-report?fbclid=IwAR2xMZr5GdD1GaNpjsXR3\_yeeIR4H9iFASfrni5HKcJVAO5oWA52bvwcZxU}.} (DTAG) states clearly that ``{\it DTAG was not tasked with evaluating any of the following: (...) Facebook’s policies with respect to “fake news” or misinformation, as neither of these categories were counted as violations within the first two versions of the Community Standards Enforcement Report.}''. Facebook's strategy to tackle ``False News'' is three fold : Remove, Reduce, Inform. It is explained via a blog post on the facebook Newsroom.\footnote{See: \href{https://about.fb.com/news/2018/05/hard-questions-false-news/}{https://about.fb.com/news/2018/05/hard-questions-false-news/}.}. Similarly, Twitter communicates about actions related to misinformation via their Twitter Safety Blog/accout\footnote{See \href{https://blog.twitter.com/en\_us/authors.TwitterSafety}{https://blog.twitter.com/en\_us/authors.TwitterSafety}.}.

{\color{pink} Say what they say they do + partnerships with fact-checkers + algorithms + community,  idea about academic community needs to be able to study this phenomenon and assess the impact of the policies, what effects they have etc. Violations fall into other categories: deceptive practices, impersonation, hate speech. }

@@

%{\color{red} Policies not specific to misinformation, but to enforce laws + things already used for terrorism and hate speech. Intro or/and Discussion. accounts: hard to say suspension for which.} 
% Misinformation : which law ? not defined ! 
%: Public content insights tool owned and operated by Facebook.
%\footnote{Public content insights tool owned and operated by Facebook.}
%: commercial content \\ database

\begin{table}[]
\centering
\begin{tabular}{|l|c|l|l|l}

\hline
&  \begin{tabular}[c]{@{}l@{}} Application Programming \\ Interface (API)  \end{tabular}                                                                                                                                                                                                                                                                                                                                                                                                                                            &    \multicolumn{1}{l|}{\begin{tabular}[c]{@{}l@{}} Web \\ Scraping \end{tabular}}                                                                                                                                                                 \\ \hline
 \includegraphics[scale=0.05]{./img/fb_logo.png} & \begin{tabular}[c]{@{}l@{}}\href{https://www.crowdtangle.com}{CrowdTangle API} \\ \href{https://buzzsumo.com}{Buzzsumo}   \end{tabular}                                                                                                                                                                                                               &      \multicolumn{1}{l|}{}    
\\ \hline
 \includegraphics[scale=0.007]{./img/tw_logo.png}  &  \href{https://developer.twitter.com/en/docs/twitter-api/early-access}{Twitter API V2} & \multicolumn{1}{l|}{\href{https://github.com/medialab/minet/blob/master/docs/cli.md\#twitter-scrape}{Minet tw scrape}}                                                                                                                                                                           \\ \hline
 \includegraphics[scale=0.03]{./img/yt_logo.png}  &  \href{https://developers.google.com/youtube/v3}{Youtube API V3}      &                                                                                                                            \multicolumn{1}{l|}{}                                                                                                                                                                           \\ \hline
\end{tabular}
\caption{Data collection}
\label{tab1}
\end{table}

@@

\begin{figure}
\centering
	\begin{multicols}{1}
		\includegraphics[scale=0.35]{./img/lifesite.jpg} 
	\end{multicols}
	\begin{multicols}{1}
		\includegraphics[scale=0.35]{./img/lifesite_rolling_7_lifesite.jpg}
	\end{multicols}
\caption{Panel (a): number of Tweets per day of the Twitter account $@Lifesite$ linked to the website lifesitenews.com from January, 2019 until April 2021. Panel (b): number of Tweets per day that have shared a lifesitenews.com URL link from January, 2019 until April 2021. }
\label{fig2}
\end{figure}

@@

\begin{figure}
	\centering
	\begin{multicols}{1}
		\includegraphics[scale=0.29]{./img/oann/fig1_oann.png}
	\end{multicols}
	\begin{multicols}{1}
		\includegraphics[scale=0.3]{./img/oann/fig2_oann.png} 
	\end{multicols}
	\caption{panel (a): Number of Youtube videos uploaded each day by the youtube channel {\it One America news Network} November 1, 2020 and January 1, 2021. Panel (b): accumulated view counts for videos. The metrics correspond to the videos’  publishing date and the data is retrieved from the youtube API with the {\it playlists} and  {\it videos} endpoints. }
	\label{fig1_oann}
\end{figure}

@@

\begin{figure}
	\centering
	\begin{multicols}{1}
		\includegraphics[scale=0.32]{./img/oann/fig3_oann.png}
	\end{multicols}

	\begin{multicols}{1}
		\includegraphics[scale=0.35]{./img/tony/fig3_tony.png}
	\end{multicols}

@@

In this section, we provide one case study of how Facebook can block a URL as part of its policy enforcement tools. The Beauty of life (\href{https://thebl.com/}{thebl.com/}) is a US-based media company that shares pro-Trump views and conspiracy theories such as QAnon.\footnote{ See \href{https://en.wikipedia.org/wiki/The\_Epoch\_Times\#Removal\_of\_The\_BL\_(The\_Beauty\_of\_Life)\_from\_Facebook}{wikipedia article}.} Facebook has announced on December $20$, $2019$ that ``The BL is now banned from Facebook'' for coordinated inauthentic behavior\footnote{\href{https://about.fb.com/news/2019/12/removing-coordinated-inauthentic-behavior-from-georgia-vietnam-and-the-us/}{https://about.fb.com/news/2019/12/removing-coordinated-inauthentic-behavior-from-georgia-vietnam-and-the-us/}.}, which includes using fake accounts that misrepresent one's identity or using methods to artificially boost the popularity of content. Coordinated inauthentic behavior is a distinct phenomenon from disinformation according to Facebook, as ``most of the content shared by coordinated manipulation campaigns isn’t probably false”.\footnote{See: \href{https://about.fb.com/news/2019/10/inauthentic-behavior-policy-update/}{https://about.fb.com/news/2019/10/inauthentic-behavior-policy-update/}.}

@@

@@

As CrowdTangle is tracking posts only from certain public groups and pages, we also used the ``/search/articles'' endpoint of the Buzzsumo API, to gather a richer Facebook dataset. We collected the engagement data for the $14$ $232$ articles crawled by Buzzsumo from the $Infowars$ website between January $1$, $2019$ and December $31$, $2020$.  \footnote{The command can be found: \href{https://github.com/medialab/truth-and-trust-online-2021/blob/master/code/collect\_facebook\_buzzsumo\_infowars\_data.py}{here}.} We observe that the articles published after May $2$, $2019$ received less Facebook engagement than the ones published before (see figure \ref{infowars2}), with a percentage change of -$97\%$ for the reactions, -$59\%$ for the shares and -$97\%$ for the comments. An increase in engagement was also observed in $2020$. It reinforces the hypothesis that Facebook reduced the reach of posts sharing Infowars links only during a few months in $2019$.

@@

@@

\begin{figure}
\centering
	\begin{multicols}{1}
		\includegraphics[scale=0.35]{./img/globalresearch/sum_globalresearch.ca_6_months.jpg} 
	\end{multicols}
	\begin{multicols}{1}
		\includegraphics[scale=0.35]{./img/globalresearch/engagement_sum_rolling_1_globalresearch.ca.jpg}
	\end{multicols}
\caption{Top panel: daily number of Tweets, excluding retweets, containing the query {\it globalresearch.ca} from January $1$, $2021$ until June $10$, $2021$. Bottom panel: engagement metrics of Tweets containing the query {\it globalresearch.ca} from January $1$, $2021$ until June $10$, $2021$. Data collected via the Twitter API v2 on June $16$, 2021.   }
\label{fig4}
\end{figure}

\begin{figure}
\centering	
	\begin{multicols}{1}
		\includegraphics[scale=0.35]{./img/globalresearch/tweet.png} 
	\end{multicols}
	\begin{multicols}{1}
		\includegraphics[scale=0.35]{./img/globalresearch/warning.png}
	\end{multicols}
\caption{}
\label{fig4bis}
\end{figure}

@@

\begin{figure}
	\centering
	\begin{multicols}{1}
		\includegraphics[scale=0.35]{./img/tweets/Capture_2021-07-01.png} 
	\end{multicols}
	\begin{multicols}{1}
		\includegraphics[scale=0.35]{./img/tweets/Capture_2021-07-01_2.png}
	\end{multicols}
	\caption{Tweet ID \href{https://twitter.com/mohsinmalvi19/status/1285866521533861888}{1285866521533861888}. Screenshots taken on July 1, 2021. }
	\label{fig_notice}
\end{figure}

@@

Youtube may provide an information panel for videos with topics that are prone to misinformation like COVID19, moon landing, and climate change.\footnote{See the section ``Information panel giving topical context'' on Youtube Help, Google accessed on June 28, 2021: \href{https://support.google.com/youtube/answer/9004474?hl=en}{support.google.com/youtube/answer/9004474?hl=en}.} Information panels provide ressources concerning a potentially controversial topic from independent third party partners or authoritative ressources. Youtube states that these panels exist regardless of the point of view expressed in a given video. In addition, these panels are not yet available in all languages and countries. %(“Information panel giving topical context”)

To further study the assignment of information panels to videos, we implemented the following exercice. We compiled a list of $171$ Youtube videos, checked by independent fact-checkers\footnote{Is it science Feedback ? if so add.} and marked as containing false or inaccurate information. We collected the information panels, when present, in each video by scrapping the content of the web and connecting to a US server. Four types of information panels were found in the list of visited videos as shown in figure\ref{fig9}:  information about COVID19, Vaccines, Climate change and US elections.

We classified the list of Youtube videos by topic based on its content as shown in table \ref{tab2}. We recorded the number of videos containing an information panel within each category. For COVID19 and vaccine related videos more than half of the videos contained an information panel. {\color{pink} Nevertheless, we noticed that some videos get uploaded multiple times by different channels under different video titles but others didn’t even though the video was the same.} In addition, we noticed for COVID19 related videos, when the video title did not include keywords like (Testing, Pandemic, COVID, coronavirus), the video might not contain a panel associated with it, and in some cases when the video title contains variations of word COVID like (C.O.V.I.D or Cv19) it wouldn’t include a panel either. Therefore, we suspect that youtube is automatically adding panels to the videos based on the video title and not the content of the video since many of the videos that didn’t have a panel had the word COVID or coronavirus or vaccine mentioned in the video itself.

For climate change we only examined $18$ misleading videos and we found that $72\%$ did not display an information panel. Lastly , for the general health category, we included the videos that were not related to COVID19 but contained misinformation concerning cures for cancer, abortion,  and viruses; no information panels were displayed for that set of Youtube videos. Therefore, it is likely that Youtube add information panels below videos conecrning controversial topics that can have misleading information like the climate change, COVID19, flat earth and  vaccine.

@@

\newpage

@@

\begin{table*}[h]
\begin{tabular}{|c|c|c|}
\hline
\multirow{3}{*}{Rules}                     & \includegraphics[scale=0.05]{./img/fb_logo.png} & \href{https://www.facebook.com/communitystandards/recentupdates/}{facebook.com/communitystandards/recentupdates/}                         \\ \cline{2-3} 
                                           & \includegraphics[scale=0.007]{./img/tw_logo.png}   & \href{https://help.twitter.com/en/rules-and-policies/twitter-rules}{help.twitter.com/en/rules-and-policies/twitter-rules}                       \\ \cline{2-3} 
                                           & \includegraphics[scale=0.03]{./img/yt_logo.png}  & \href{https://www.youtube.com/intl/en\_us/howyoutubeworks/policies/community-guidelines/}{youtube.com/intl/en\_us/howyoutubeworks/policies/community-guidelines/} \\ \hline
\multirow{3}{*}{\begin{tabular}[c]{@{}l@{}}  Rules \\ enforcement \end{tabular}}         & \includegraphics[scale=0.05]{./img/fb_logo.png}  & \href{https://transparency.fb.com/data/community-standards-enforcement/}{transparency.fb.com/data/community-standards-enforcement/}                 \\ \cline{2-3} 
                                           & \includegraphics[scale=0.007]{./img/tw_logo.png}   & \href{https://transparency.twitter.com/en/reports/rules-enforcement.html}{transparency.twitter.com/en/reports/rules-enforcement.html}                \\ \cline{2-3} 
                                           & \includegraphics[scale=0.03]{./img/yt_logo.png}  & \href{https://transparencyreport.google.com/youtube-policy/}{transparencyreport.google.com/youtube-policy/}                              \\ \hline
\multirow{3}{*}{\begin{tabular}[c]{@{}l@{}}  Transparency \\ center \end{tabular}}       & \includegraphics[scale=0.05]{./img/fb_logo.png} & https://transparency.fb.com/data/                                                  \\ \cline{2-3} 
                                           & \includegraphics[scale=0.007]{./img/tw_logo.png}   & \href{https://transparency.twitter.com/en/reports.html}{transparency.twitter.com/en/reports.html}                                  \\ \cline{2-3} 
                                           & \includegraphics[scale=0.03]{./img/yt_logo.png}  & \href{https://transparencyreport.google.com/?hl=en}{transparencyreport.google.com/?hl=en}                                      \\ \hline
\multirow{3}{*}{\begin{tabular}[c]{@{}l@{}}  Policy regarding \\  Covid-19 \end{tabular}} & \includegraphics[scale=0.05]{./img/fb_logo.png} & https://www.facebook.com/help/230764881494641/                                     \\ \cline{2-3} 
                                           & \includegraphics[scale=0.007]{./img/tw_logo.png}   & \href{https://help.twitter.com/en/rules-and-policies/medical-misinformation-policy}{help.twitter.com/en/rules-and-policies/medical-misinformation-policy}       \\ \cline{2-3} 
                                           & \includegraphics[scale=0.03]{./img/yt_logo.png}  & \href{https://support.google.com/youtube/answer/9891785}{support.google.com/youtube/answer/9891785}                                 \\ \hline
\multirow{3}{*}{\begin{tabular}[c]{@{}l@{}}  Fact-checking \\ policy \end{tabular}} & \includegraphics[scale=0.05]{./img/fb_logo.png} & \href{https://www.facebook.com/journalismproject/programs/third-party-fact-checking/how-it-works}{facebook.com/journalismproject/programs/third-party-fact-checking/how-it-works}                                    \\ \cline{2-3} 
                                           & \includegraphics[scale=0.007]{./img/tw_logo.png}   & x       \\ \cline{2-3} 
                                           & \includegraphics[scale=0.03]{./img/yt_logo.png}  & \href{https://support.google.com/youtube/answer/9229632}{support.google.com/youtube/answer/9229632}                                  \\ \hline

\end{tabular}
\caption{Summary of ressources, last accessed on July 5, 2021. }
\label{summary}
\end{table*}

%https://www.facebook.com/journalismproject/programs/third-party-fact-checking/how-it-works
\end{document}
